\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-13 jss/article.tex
correcting

Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger). This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.

\subsection{Binomial: 18 Baseball Data}
This dataset contains information about batting averages of 18 major league players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975). Also, it has two covariates, League and Position, showing in which league and in which position each player was playing. In this paper, we will use Position for a tutorial purpose. For convenience, we transform this variable into a binary indicator, which is 1 if a player was a outfielder and 0 otherwise. The code below shows a way to make inputs. If we have more than one covariate, for example, \code{x1} and \code{x2}, then `\code{R> x <- cbind(x1, x2)}' will be the right input of the \code{gbp} function.
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
\end{CodeInput}
\end{CodeChunk}
The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown parameter $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$. This dataset is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.

@@

where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients. Note that if there is no covariate then $m$ is 1 for an intercept term, making $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$. For reference, a paramter with a zero subscript, $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution. Also,  Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution.
\begin{equation}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})\sigma^{2}_{j}),
\end{equation}
where $B_{j}\equiv\frac{\sigma^{2}_{j}}{\sigma^{2}_{j} + A},~j=1, \ldots, 8$, is called a shrinkages.

\subsection[Poisson-Gamma]{Poisson-Gamma}
\code{gbp} is also able to build a Poisson-Gamma multi-level model on the 31 hospital data. Note that a constant multiplied to the notation representing Gamma distribution below is a scale and a square bracket below indicates [mean, variance] of distribution. And for notational consistency, let's define $y_{j}\equiv \frac{z_{j}}{n_{j}}$ for all $j$.
\begin{equation}
z_{j}\vert \lambda_{j} \stackrel{ind}{\sim}\textrm{Poisson}(n_{j}\lambda_{j}),
\end{equation}
\begin{equation}
\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(\lambda_{0j}r)\sim \textrm{Gamma}[\lambda_{0j}, ~\frac{\lambda_{0j}}{r}],
\end{equation}

@@

where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0j}$,  $B_{j}\equiv \frac{r}{r+n_{j}}$, and $y_{j}\equiv \frac{z_{j}}{n_{j}}$, $j=1, \ldots, 31$.

@@

\subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
Hyper-prior distribution indicates a distribution of the second-level parameters, which plays an important role in deriving a full posterior distribution of all the parameters. \code{gbp} sets a non-informative distribution on second-level parameters to let the data speak more about their estimation.
\begin{equation}
\beta \sim \textrm{Uniform on}~ \mathbf{R}^{m},~~A ~(\textrm{or}~ \frac{1}{r})\sim \textrm{Uniform}(0, \infty),
\end{equation}

where $m$ is the number of regression coefficients. For $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets informative as number of groups increases. Another flat prior on the hyper-prameter $A$ (or $1/r$) that we suggest here will guarantee a posterior propriety under the moderate conditions and will give users a good repeated sampling property.
\\

\section[Estimation]{Estimation}
\subsection[Shrinkage Estimation]{Shrinkage Estimation}
Estimating shrinkage is a key part of our work because as we can see the posterior means in (3), (6), and (9) are a linear function of shrinkage and the posterior variances are also a linear (Gaussian), quadratic (Poisson), or cubic (Binomial) function of shrinkage. Once we estimate it, we can approximate the posterior moments given only data by Adam's law, for example, $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ for Gaussian model and by Eve's law, for instance, $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$
\subsection[ADM]{Adjustment for Density Maximization}
When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv\frac{\sigma^{2}}{\sigma^{2}+A}=B_{j}(A)$ for Gaussian and $B_{j}\equiv\frac{r}{r+n_{j}}=B_{j}(r)$ for Poisson and Binomial models.
\\

In this case, one way is to obtain an MLE of the variance component with its asymptotic Normal distribution and then to use Delta method for asymptotic Normal distribution of shrinkage. But is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1?
\\

Here the adjustment for density maximization (Morris and Tang, 2011), called ADM, comes. It assumes the Beta distribution for shrinkage, which the authors believe is a much better approximation for it, and estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$.

\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
After estimating two posterior moments, \code{gbp} reasonably approximates posterior distribution given only data, \emph{i.e.}, ($\mu_{j}\vert \textrm{data}$), ($\lambda_{j}\vert \textrm{data}$), or ($p_{j}\vert \textrm{data}$), by matching two moments with its parameters. The reason we said `reasonablely approximates' is that it is hard to find a closed form of posterior distribution given only data unless it is a Gaussian model. So, we assumed $(p_{j}\vert \textrm{data})$ had also Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textrm{data})$ and $Var(p_{j}\vert \textrm{data})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.

\section[Method Check]{Method Check}
Like the two sides of the same coin, checking a statistical model always comes with fitting a model. If a fitted model cannot pass a checking process, we usually go back to the fitting process and come back to checking process iteratively. In this sense, checking a fitted model is an interactive procedure for the model justification.
\\

There are two kinds of model justification process; one is a model check and the other is a method check. The model check is for the justification of a hierarchical modeling on a specific dataset. One possible question is, ``Can this dataset benefit from such a modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $(z_{j}\vert \beta, r)\sim\textrm{Negative-Binomial}$, for Poisson data to justify the second-level hierarchy. They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
\\

Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates. ``Does the confidence interval obtained via this Bayesian model-fitting process achieve pre-specified 100($1-\alpha$)\% confidence level for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point. From now on, all the explanations will be based on the Binomial model.

\subsection{Pseudo-data Generation Process}
Figure 1 will be helpful to understand this process. As we can see in (8), the distribution of each true parameter ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(m\times1)}$, where $m$ is the number of regression coefficients. Once we fix these hyper-parameters at specific values, we can generate true parameters. Suppose we sampled 500 $\textbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\textbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$. Then, we can also generate $\{\textbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-dataset and $j$ does $j$-th player. Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\textbf{z}^{(i)}_{(18\times1)}, \textbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500*18 interval estimates. Taking the first player as an example, we have 500 pairs of ($z_{i1}$, $p_{i1}$), $i=1,\ldots, 500$, and 500 interval estimates.
\begin{figure}[h]
\begin{center}
\includegraphics[width=5cm]{process.png}
\caption{Pseudo-data generating process}
\end{center}
\end{figure}

@@

\subsection{Rao-Blackwellized Coverage Probability}
Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were fixed at first (see 5.1) and $z_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates (numeric values) on the $i$-th dataset. We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ in (9). Then, we can estimate the first player's coverage probability, for instance, by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
\section[Example]{Example}
\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
If you, living in the New York state (NY), were suffering from severe coronary heart disease (hopefully not), and were supposed to receive the coronary artery bypass graft (CABG) surgery, your concern might be each hospital's abililty to handle this surgery.
\\

For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths within a month of CABG surgeries and total number of patients receiving CABG surgeries in each hospital. In addition, suppose you could obtaion the state-level death rate of this surgery while you were looking for such information, which was 0.02. From this point, there are a lot of ways to explore those data to have an idea about each hospital's ability. 
\\

One way we suggest here is a hierarchical modeling assuming that there is a bigger population-level hierarchy. In this case, for example, we presume that there is a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY. Then, we can consider the true death rates of those 31 hospitals were sampled from this state-level population distribution whose mean is 0.02. The validity of such an assumption can be checked (Christiansen and Morris, 1996).
\\

>>>>

Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger). This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.

\subsection{Binomial: 18 Baseball Data}
This dataset contains information about batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975). Also, it has two covariates, League and Position, showing in which league and in which position each player was playing. In this paper, we will use Position for a tutorial purpose. For convenience, we transform this variable into a binary indicator, which is 1 if a player was a outfielder and 0 otherwise. The code below shows a way to make inputs. If we have more than one covariate, for example, \code{x1} and \code{x2}, then `\code{R> x <- cbind(x1, x2)}' will be the right input of the \code{gbp} function.
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
\end{CodeInput}
\end{CodeChunk}
The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown true batting average $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$. This dataset is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.

@@

where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients. Note that if there is no covariate then $x_{j, (1\times1)}=1$ for an intercept term and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution. For reference, a paramter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean. Also,  Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution, which is the same as (1) $\times$ (2) up to a normalizing constant.
\begin{equation}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})\sigma^{2}_{j}),
\end{equation}
where $B_{j}\equiv\frac{\sigma^{2}_{j}}{\sigma^{2}_{j} + A},~j=1, \ldots, 8$, is called a shrinkages.

\subsection[Poisson-Gamma]{Poisson-Gamma}
\code{gbp} is also able to build a Poisson-Gamma multi-level model on the 31 hospital data. Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket below indicates [mean, variance] of distribution. And for notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ for all $j$.
\begin{equation}
z_{j}\vert \lambda_{j} \stackrel{ind}{\sim}\textrm{Poisson}(n_{j}\lambda_{j}),
\end{equation}
\begin{equation}
\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(\lambda_{0j}r)\sim \textrm{Gamma}[\lambda_{0j}, ~\frac{\lambda_{0j}}{r}],
\end{equation}

@@

where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0j}$,  $B_{j}\equiv r / (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1, \ldots, 31$.

@@

\subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
Hyper-prior distribution indicates a distribution of the second-level parameters, which plays an important role in deriving a full posterior distribution of all the parameters. \code{gbp} sets non-informative distributions on second-level parameters to let the data speak more about their estimation.
\begin{equation}
\beta \sim \textrm{Uniform on}~ \mathbf{R}^{m},~~A ~(\textrm{or}~ \frac{1}{r})\sim \textrm{Uniform}(0, \infty),
\end{equation}

where $m$ is the number of regression coefficients. For $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases. Another flat prior on the second-level variance component  $A$ (or $1/r$) that we suggest here will guarantee a posterior propriety under the moderate conditions and will bring a good repeated sampling property to us.
\\

\section[Estimation]{Estimation}

\subsection[Shrinkage Estimation]{Shrinkage Estimation}
Estimating shrinkage is a key part of our hierarchical modeling. As we can see in (3), (6), and (9), the posterior means are a linear function of shrinkage and the posterior variances are also a linear (Gaussian), quadratic (Poisson), or cubic (Binomial) function of shrinkage. It implies that we cannot obtain $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ without appropriate shrinkage estimation.

\subsection[ADM]{Adjustment for Density Maximization}
When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv\frac{\sigma^{2}}{\sigma^{2}+A}=B_{j}(A)$ for Gaussian and $B_{j}\equiv\frac{r}{r+n_{j}}=B_{j}(r)$ for Poisson and Binomial models.
\\

In this case, the most common way is to obtain an MLE of the variance component with its asymptotic Normality and then to use Delta method for asymptotic Normal distribution of shrinkage, \emph{i.e.}, $\hat{B}_{j, MLE}=B_{j}(\hat{A}_{MLE})$. But is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1? Why do we fit a logistic regression, such as logit($p$) = $x^{T}\beta$, instead of fitting a linear regression, $p = x^{T}\beta$?
\\

Here the adjustment for density maximization (Morris and Tang, 2011), called ADM, comes. It assumes the Beta distribution for shrinkage because this distribution is also defined between 0 and 1. In the end, ADM  estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause. Please refer to Morris and Tang (2011) for more apparent advantages for using ADM.
\\

Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only data. Taking the Normal model as an example,  $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Adam's law and $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Eve's law. Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are a function of shrinkage in (3) and Adam's and Eve's laws are taking conditional expectation and variance over it given data.

\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
After estimating two posterior moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, \code{gbp} reasonably approximates a posterior distribution given data, \emph{i.e.}, $p_{j}\vert \textbf{z}$ (or $\mu_{j}\vert \textbf{y}$, $\lambda_{j}\vert \textbf{z}$), by matching these two moments with its parameters. To be specific, we assumed $p_{j}\vert \textbf{z}$ had another Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.

\section[Method Check]{Method Check}
Like the two sides of the same coin, checking a statistical model always comes with fitting a model. If a fitted model cannot pass a checking process, we usually go back to the fitting process and come back to the checking process iteratively. In this sense, checking a fitted model is an interactive procedure for the model justification.
\\

There are two kinds of model justification process; one is a model check and the other is a method check. The model check is for the justification of a hierarchical modeling on a specific dataset. One possible question is, ``Can this dataset benefit from such a multi-level modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy. They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
\\

Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates, the final product of this multi-level modeling. ``Does the confidence interval obtained via this Bayesian model-fitting process achieve pre-specified 100($1-\alpha$)\% confidence level for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point. From now on, all the explanations will be based on the Binomial model.

\subsection{Pseudo-data Generation Process}
Figure 1 will be helpful to understand this process. As we can see in (8), the distribution of each true batting average ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(m\times1)}$, where $m$ is the number of regression coefficients. So, once we fix these hyper-parameters at specific values, we can generate true batting averages. Suppose we sampled 500 $\mathbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\mathbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (8), where $r$ and $\beta$ are given. Then, we can also generate $\{\mathbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-dataset and $j$ does $j$-th player. Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\mathbf{z}^{(i)}_{(18\times1)}, \mathbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500$\times$18 interval estimates.  After this generating process, as for the first player, we will have 500 pairs of ($z_{i1}$, $p_{i1}$) and 500 interval estimates, ($\hat{p}_{i1, low}, \hat{p}_{i1, upp}$), $i=1, \ldots, 500$.
\begin{figure}[h]
\begin{center}
\includegraphics[width=5cm]{process.png}
\caption{Pseudo-data generating process}
\end{center}
\end{figure}

@@

\subsection{Rao-Blackwellized Coverage Probability}
Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates on the $i$-th dataset. We can calculate this probability  because we know the distribution of $p_{ij} \vert z_{ij}, r, \beta$ in (9). Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ because we know $r$ and $\beta$. Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is way more accurate than the previous one.
\section[Example]{Example}
\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease (hopefully not). If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery. On top of that, if you can figure out each hospital's abililty to handle this surgery, it will be useful for your decision to choose a hospital.
\\

For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths within a month of CABG surgeries and total number of patients receiving CABG surgeries in each hospital. In addition, while you were looking for such information, suppose you could know that the  state-level death rate per exposure of this surgery in the past ten years was 0.02. 
\\

The multi-level modeling that assumes a bigger population-level hierarchy will be insightful in this problem. Here, we presume a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY. This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution whose mean is 0.02. For reference, a model check can be useful for evaluating the validity of such a view point (Christiansen and Morris, 1996). 
\\
